Algorithm explanation

### 2013-08-21 article/algo.tex
Clarify TODOs
Algorithm explanation and pseudo-code

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}

@@

@@

@@

We first propose an algorithm to compute a simple solution for the given
$G$ if one exists. Later we add modifications to the algorithm if a
simple solution does not exist.
Our algorithm works in a constructive manner. List 1 shows the
pseudo-code of our algorithm.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}

@@

\begin{align*}
\text{Constraint:} \\
TODO \\
\\
\text{Unsatisfiable core:} \\
TODO
\end{align*}

This time, the unsatisfiable core contains the constraints that
originate from

TODO

@@

Finally, we obtain the following constraint:

TODO

@@

We first propose an algorithm to compute a simple solution for the
given $G$ if one exists.  Later we add modifications to the algorithm
for the case that a simple solution does not exist.

Our algorithm works in a constructive manner.
Algorithm~\ref{alg:solveHorn} shows the pseudo-code of our algorithm.

\newcommand{\solveHorn}{\ensuremath{\mbox{\sc SolveHornGraph}}}
\newcommand{\genConstr}{\ensuremath{\mbox{\sc GenerateConstraint}}}

\begin{algorithm}
\caption{$ \solveHorn (G) $}\label{alg:solveHorn}
\begin{algorithmic}
\STATE {$v_\bot \gets $ the root node of $G$}
\STATE {$visited \gets \left\lbrace v_\bot \right\rbrace$}

\STATE {$C \gets \genConstr (v_\bot, visited)$}
\STATE {$c_{v_\bot} \gets C(v_\bot)$}
\IF {$c_{v_\bot}$ is satisfiable}
  \IF {$visited$ contains all predicate variable vertices}
    \STATE {$visited \gets a$}
    \COMMENT {build solution}
  \ELSE
    \STATE {$visited \gets a$}
  \ENDIF
\ELSE
  \STATE {$\mathcal{UC} \gets $ unsatisfiable core for $c_{v_\bot}$}
\ENDIF
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{$ \genConstr (v, visited) $}\label{alg:genConstr}
\begin{algorithmic}
\STATE {$m \gets \emptyset$}
\FORALL {$v_\Rightarrow \in preds(v)$}
  \FORALL {$v_p \in preds(v_\Rightarrow)$}
    \STATE { $ l := \varphi (v_p) $ }
    \IF {$l$ is a predicate variable}
      \STATE {$m' \gets \genConstr (v_p) $}
      \STATE {$m \gets m \cup m'$}
    \ELSE
      \STATE { $id$ }
    \ENDIF
  \ENDFOR
\ENDFOR
\end{algorithmic}
\end{algorithm}

The construction of the algorithm is two fold.
\begin{itemize}
\item \textbf{Iterative Constraint Building} The process starts from
  generating the weakest constraint that the graph allows and
  iteratively strengthen a constraint until the strongest one.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, restructure the input Horn graph
  to enlarge the solution template.
\end{itemize}

All vertices with predicate variable labels are assigned a simple
template.  For a vertex with a label $P(\mathbf{x})$, the algorithm
assigns a template $\mathbf{a_P} \mathbf{x} + b_P \leq 0$.  Parameters
$\mathbf{a_P}$ and $b_P$ are specified by a linear constraint.

For each predicate variable vertex, build a linear constraint
  that parameters in predicate variable templates must satisfy.

$\genConstr$ procedure produces the constraint for all vertices

In this algorithm, vertices with a predicate variable label must have
a simple solution assignment.
